### 2021-04-20 paper/ase21/conclusion.tex
[ASE21] Till conclusion

\section{Conclusion}\label{sec:conclusion}
Since an incorrect description in ECMAScript can lead to the wrong JavaScript
engine implementations, checking the correctness of ECMAScript is essential.
Since ECMAScript is annually released and developed in open process, it becomes
more labor-intensive and error-prone.  To alleviate the problem, we propose
$\tool$, a JavaScript Specification Type Analyzer using Refinement.  It is the
first tool that performs \textit{type analysis} on JavaScript specifications and
detects specification bugs using a \textit{bug detector}.  Moreover, to increase
precision of type analysis, we present \textit{condition-based refinement} for
type analysis, which prunes out infeasible abstract states using conditions of
assertions and branches.  We evaluated $\tool$ with all 864 versions in the
official ECMAScript repository for the recent three years from 2018 to 2021.
Our tool took \inred{230} seconds on average to perform type analysis for each
version, and detected \inred{200} type-related specification bugs with
\inred{50.3}\% precision; \inred{91} out of \inred{200} bugs are true bugs.
Among them, \inred{14} bugs are newly detected by $\tool$ and the committee
confirmed all of them.

>>>>

\section{Conclusion}\label{sec:conclusion}
Since an incorrect description in ECMAScript can lead to the wrong JavaScript
engine implementations, checking the correctness of ECMAScript is essential.
Since ECMAScript is annually released and developed in open process, it becomes
more labor-intensive and error-prone.  To alleviate the problem, we propose
$\tool$, a JavaScript Specification Type Analyzer using Refinement.  It is the
first tool that performs \textit{type analysis} on JavaScript specifications and
detects specification bugs using a \textit{bug detector}.  Moreover, to increase
precision of type analysis, we present \textit{condition-based refinement} for
type analysis, which prunes out infeasible abstract states using conditions of
assertions and branches.  We evaluated $\tool$ with all 864 versions in the
official ECMAScript repository for the recent three years from 2018 to 2021.
Our tool took \inred{136.0} seconds on average to perform type analysis for each
version, and detected \inred{177} type-related specification bugs with
\inred{52.0}\% precision; \inred{92} out of \inred{177} bugs are true bugs.
Among them, \inred{14} bugs are newly detected by $\tool$, and the committee
confirmed all of them.

### 2021-04-20 paper/ase21/eval.tex
[ASE21] Till conclusion

To evaluate $\tool$, we answer the following research questions:
\begin{itemize}
  \item RQ1. \textbf{(Performance)} How long does $\tool$ take to perform type
    analysis for JavaScript specifications?
  \item RQ2. \textbf{(Precision)} How many type-related specification bugs
    detcted by $\tool$ are true bugs?
  \item RQ3. \textbf{(Effect of Refinement)} Does the condition-based refinement
    improve the analysis precision with endurable performance degradation?
  \item RQ4: \textbf{(Detection of New Bugs)} Does $\tool$ detect new
    specification bugs in the latest version of ECMAScript?
\end{itemize}
The draft of the next version of ECMAScript (ES12, 2021) is fixed on March 9,
2021.  Thus, we targeted all different 864 versions existed in the official
ECMAScript repository~\footnote{https://github.com/tc39/ecma262} for the recent
three years from January 1, 2018 to March 9, 2021.  We performed our experiments
on five Ubuntu machines equipped with 4.2GHz Quad-Core Intel Core i7 and 32GB of
RAM.

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{img/author}
  \caption{The creators and resolvers of true bugs.}
  \label{fig:author}
  \vspace*{-1.5em}
\end{figure}

@@

Moreover, we extended $\tool$ to automatically extract more statistics of
detected true bugs.  \inred{First, we checked that true bugs are created or
resolved by whom as described in Figure~\ref{fig:author}.  Among \inred{92}
true bugs, \inred{47} bugs are \textit{inherited}, which means that they are
created before 2018, and \inred{14} bugs are newly found

\inred{20} bugs, only \inred{20} bugs are created by members of the Ecma
Technical Committee 39 (TC39) but others (\inred{20} bugs) are created by
outside contributors not committee members.  On the other hand, most of them
(\inred{20} bugs) are resolved by the committee members but only \inred{20} bugs
are resolved by non-committee contributors.  Other \inred{14} bugs are newly
found and we will explain their details in Section~\ref{sec:new-bug}.}  Another
statistic of true bugs is Time to Live (TTL) that denotes how many days
specification bugs existed.  Figure~\ref{fig:ttl} describes TTLs of true bugs;
the left chart (Figure~\ref{fig:ttl}(a)) depicts their periods sorted by their
creation time, and the right chart (Figure~\ref{fig:ttl}(b)) depicts the
histogram of TTLs in a logarithmic scale.  The average days of TTL is
\inred{300.0} even though we assume that \inred{20} inherited bugs are created
in January 1, 2018.  The maximum length of TTL is \inred{1,000} and the
corresponding bug is inherited and not yet resolved in the latest version.  We
manually investigated its creation time in the history of the official
repository, and we discovered that it was created at the initial commit of the
open development process in September 22, 2015.  It means that the bug actually
existed for \inred{3,000} days.

@@

We evaluated the effectiveness of condition-based refinement based on how much
it improved analysis precision without significant performance degradation.  To
compare performance and precision of analysis without refinement
(\stextsf{no-refine}) and with refinement (\stextsf{refine}), we also performed
$\tool$ without refinement for 864 versions of ECMAScript.

For performance, Figure~\ref{fig:performance-compare} describes the comparison
of iterations and analysis time without refinement and with refinement; the left
charts (Figure~\ref{fig:performance-compare}(a) and
\ref{fig:performance-compare}(c)) are histograms of iterations and analysis
time, and the right charts (Figure~\ref{fig:performance-compare}(b) and
\ref{fig:performance-compare}(d)) are scatter charts for their ratio.  Without
refinement, type analysis took \inred{234.3} seconds with \inred{232}K
iterations on average.  With refinement, it took \inred{234.3} seconds with
\inred{232}K iterations on average.  For each version, analysis time is
increased at least \inred{2.3}x, at most \inred{2.3}x, and \inred{2.3}x on
average, and the number of iterations is increased at least \inred{2.3}x, at
most \inred{2.3}x, and \inred{2.3}x on average.

Table~\ref{table:precision} shows the analysis precision without refinement,
with refinement, and their difference.  The refinement improved the analysis
precision from \inred{23.2}\% to \inred{23.3}\% by removing \inred{10} false
bugs and to detect \inred{10} more true bugs.  \inred{(\todo: investigate the result for
each checker.)}

@@

Among \inred{91} true bugs detected by $\tool$, \inred{14} bugs are newly
detected and still exist in the latestest version of ECMAScript.
Table~\ref{table:new-bug} summarizes the bugs categorized by their kinds and
related JavaScript language features. It includes their TTLs, and we manually
investigated their extact creation time if they are created before 2018.  We
reported the newly detected bugs to TC39; all of them are confirmed by the
committee and will be fixed in ECMAScript 2022 (ES13).

ES12-1 contains three bugs that are due to the duplicated definition of
variables in three different algorithms for \jscode{case} blocks of
\jscode{switch} statements: \code{hasDuplicates} in
\textbf{ContainsDuplicateLabels}, and \code{hasUndefinedLabels} in
\textbf{ContainsUndefinedBreakTarget} and
\textbf{ContainsUndefinedContinueTarget}.  Each \jscode{case} block optionally
contains \jscode{case} clauses, and three algorithms perform additional stpes
including to define \code{hasDuplicates} (or \code{hasUndefinedLabels}) when the
clauses exist at the beginning.  However, the exactly same variable is defined
again after the coditionally additional steps.  It means that the semantics of
\jscode{case} blocks having \jscode{case} clauses always have reference for
already defined variable \code{hasDuplicates} (or \code{hasUndefinedLabels}).
ES12-2 also contains three bugs caused by the exactly same reasons in same
abstract algorithms for \jscode{try} statements.

The bug in ES12-3 is a reference bug for already defined variable \code{index}
in the abstract algorithm \textbf{CreateMappedArgumentsObject}.  For each
function call in JavaScript programs, an \jscode{arguments} object is created by
\textbf{CreateMappedArgumentsObject}.  In the algorithm, the variable
\code{index} is defined to handle the index of a given list of arguments.
However, the variable is defined twice in step 14 and 17 of the algorithm.

ES12-4 contains two reference bugs for already defined variable \code{succeeded}
in \textbf{DefineOwnProperty} of \jscode{Array} objects and
\textbf{ArraySetLength}.  The \jscode{Array} objects are exotic, which means
that they are not ordinay objects and have special algorithms for specific
behaviors.  The two algorithms are wrapper algorithms of
\textbf{OrdinaryDefineOwnProperty} which updates object properties.  They define
the variable \code{succeeded} to represent the result of
\textbf{OrdinaryDefineOwnProperty}.  However, the variable is defined twice in a
specific condition.

@@

The bug in ES12-6 is a reference bug for unknown variable \code{ClassHeritage}
in \textbf{Contains} for tails of \jscode{class} declarations.  A tail of
\jscode{class} declaration consists of an optional class heritage with
\jscode{extneds} keyword and a class body enclosed by curly braces.  When the
optional class heritage does not exist, the variable \code{ClassHeritage} is not
defined but the \textbf{Contains} algorithm tries to access it without any check
of its existence.

>>>>

To evaluate $\tool$, we answer the following research questions:
\begin{itemize}
  \item RQ1. \textbf{(Performance)} How long does $\tool$ take to perform type
    analysis for JavaScript specifications?
  \item RQ2. \textbf{(Precision)} How many type-related specification bugs
    detected by $\tool$ are true bugs?
  \item RQ3. \textbf{(Effect of Refinement)} Does the condition-based refinement
    improve the analysis precision with endurable performance degradation?
  \item RQ4: \textbf{(Detection of New Bugs)} Does $\tool$ detect new
    specification bugs in the latest version of ECMAScript?
\end{itemize}
The draft of the next version of ECMAScript (ES12, 2021) is fixed on March 9,
2021.  Thus, we targeted all different 864 versions existed in the official
ECMAScript repository~\footnote{https://github.com/tc39/ecma262} for the recent
three years from January 1, 2018 to March 9, 2021.  We performed our experiments
on five Ubuntu machines equipped with 4.2GHz Quad-Core Intel Core i7 and 32GB of
RAM.

@@

% \begin{table}
%   \centering
%   % \includegraphics[width=\columnwidth]{img/author}
%   \caption{The creators and resolvers of true bugs.}
%   \label{fig:author}
%   \resizebox{\columnwidth}{!}{$
%     \inred{
%     \begin{array}{c?r|r|r|r|r|r?c?c}
%       \textbf{Rank} >
%       & 0 & 10 & 20 & 30 & 40 & 50
%       & \multicolumn{1}{c?}{\multirow{2}{*}{\textbf{Total}}}
%       & \multicolumn{1}{c}{\multirow{2}{*}{\textbf{Unknown}}}\\\cline{1-7}
%       \textbf{Rank} \leq
%       & 10 & 20 & 30 & 40 & 50 & 60
%       & & \\
% 
%       \specialrule{.1em}{.0em}{.0em}
% 
%       \textbf{\# Created}
%       & 23 & 4 & 1 & 14 & 2 & 1
%       & 45 & 46\\\hline
%       \textbf{\# Resolved}
%       & 57 & 6 & 12 & 2 & 0 & 0
%       & 77 & 14\\
% 
%     \end{array}
%     }
%   $}
%   \vspace*{-1em}
% \end{table}

@@

To understand the severity of detected true bugs, we extended $\tool$ to
automatically extract when they are created and resolved in the ECMAScript
official repository.  We defined that a bug is \textit{created} when it exists
in a certain version but does not exist in the right before version, it is
\textit{resolved} vice versa, and the \textit{Time to Live (TTL)} of a bug is
how many days they last.  Figure~\ref{fig:ttl} describes TTLs of true bugs; the
left chart (Figure~\ref{fig:ttl}(a)) depicts their periods sorted by their
creation time, and the right chart (Figure~\ref{fig:ttl}(b)) depicts the
histogram of TTLs in a logarithmic scale.  Among \inred{92} true bugs,
\inred{47} bugs are \textit{inherited}, which means that they are created before
2018, and \inred{14} bugs still existed in the latest ECMAScript thus they are
newly detected bugs by $\tool$.  We will discuss details of \inred{14} newly
found bugs in Section~\ref{sec:new-bug}.  Even though we assume that \inred{47}
inherited bugs are created in January 1, 2018, the average TTL is \inred{409.5}
and the maximum TTL is \inred{1,164}.  All bugs having the maximum TTL are
inherited and newly detected bugs.

We investigated \inred{85} false-positive bugs to reason about why they are
detected by $\tool$.  Among them, \inred{30} bugs are caused by the failed
extraction of mechanized specification because of wrong writing styles.  For
example, ECMAScript is written in HTML and $\jiset$ extracts abstract algorithms
based on \code{emu-alg} HTML tags.  However, several abstract algorithms are
defined with the opening tag \code{<emu-alg>} but without the closing tag
\code{</emu-alg>}.  Thus, $\jiset$ fails to extract them and it causes
false-positive bugs.  The remaining \inred{55} bugs are caused by imprecise type
analysis results.  Among them, \inred{20} bugs are caused by imprecise analysis
for conditions of assertions and branches strongly related with specific
function calls.  For example, consider the following algorithm step in the
algorithm \textbf{GetValue}:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \includegraphics[width=0.7\columnwidth]{img/adv-refine-example}
  \vspace*{-0.5em}
\end{figure} \noindent
Since the algorithm \textbf{IsUnresolvableReference} always returns
$\code{false}$ when the $\code{Base}$ field of a given reference record is
$\nconst{unresolvable}$, the field access \code{V.Base} never be
$\nconst{unresolvable}$ on line 4.a.  However, the abstract environment in type
analysis only stores that the variable $\code{V}$ has the $\code{Reference}$
type thus $\nconst{unresolvable}$ is also passed as the argument of
\textbf{ToObject}.  We believe that more advanced refinement technique can
resolve this problem by pruning out infeasible field types depending on specific
contexts.

@@

We evaluated the effectiveness of condition-based refinement based on how much
it improved analysis precision without significant performance degradation.  We
performed $\tool$ without refinement (\stextsf{no-refine}) for 864 versions of
ECMAScript, and compared their analysis results with the analysis with
refinement (\stextsf{refine}).

For performance, Figure~\ref{fig:performance-compare} describes the comparison
of iterations and analysis time without refinement and with refinement; the left
charts (Figure~\ref{fig:performance-compare}(a) and
\ref{fig:performance-compare}(c)) are histograms of iterations and analysis
time, and the right charts (Figure~\ref{fig:performance-compare}(b) and
\ref{fig:performance-compare}(d)) are scatter charts for their ratio.  Without
refinement, type analysis took \inred{90.9} seconds with \inred{259.1}K
iterations on average.  For each version, the number of iterations is increased
at least \inred{0.99}x, at most \inred{1.36}x, and \inred{1.16}x on average, and
the analysis time is increased at least \inred{1.05}x, at most \inred{1.41}x,
and \inred{1.98}x on average.

Table~\ref{table:precision} shows the analysis precision without refinement,
with refinement, and their difference.  The refinement improved the analysis
precision from \inred{30.4}\% to \inred{52.0}\% by removing \inred{122}
false-positive bugs and to detect \inred{one} more true bug.  Among six
difference bug kinds, the most significant improvement is about non-numeric
operand bugs (\stextsf{NoNumber}) from \inred{3.1}\% to \inred{33.3}\%
by removing \inred{59} false-positive bugs.  The refinement technique
successfully prunes out non-numeric values in conditions for numeric types.
The refinement also significantly increased the analysis precision for unknown
variable bugs (\stextsf{UnknownVar}) and assertion failures
(\stextsf{Assertion}) by removing \inred{28} and \inred{26} false-positive bugs,
respectively.  However, there is no effect of refinement to detect missing
parameter bugs (\stextsf{MissParam}) because it is possible to precisely analyze
possible callee functions for each function invocation without condition-based
refinement.

@@

Among \inred{92} true bugs detected by $\tool$, \inred{14} bugs are newly
detected and still exist in the latest version of ECMAScript.
Table~\ref{table:new-bug} summarizes the bugs categorized by their kinds and
related JavaScript language features and it also contains their TTLs. We
manually investigated their exact creation time if they are created before
2018.  Except two bugs in ES12-8, all bugs were introduced in the initial
commit of the open development on September 22, 2015.  Thus, 12 newly detected
bugs last for 1,966 days until March 9, 2021.  The other two bugs in ES12-8 were
created when a contributor introduced the prefixes \textbf{?} and \textbf{!}
on December 16, 2015 thus it last for 1,910 days.  We reported the newly
detected bugs to TC39; all of them are confirmed by the committee and will be
fixed in ECMAScript 2022 (ES13).

ES12-1 contains three bugs that are due to the duplicated definition of
variables in three different syntax-directed algorithms for \jscode{case} blocks
of \jscode{switch} statements: \code{hasDuplicates} in
\textbf{ContainsDuplicateLabels}, and \code{hasUndefinedLabels} in
\textbf{ContainsUndefinedBreakTarget} and
\textbf{ContainsUndefinedContinueTarget}.  A \jscode{case} block optionally
contains \jscode{case} clauses.  In the beginning of three algorithms,
\code{hasDuplicates} (or \code{hasUndefinedLabels}) is defined if the clauses
exist.  However, the exactly same variable is defined again after this
conditional steps.  It means that three algorithms for \jscode{case} blocks
having \jscode{case} clauses always have already defined variable bugs for
\code{hasDuplicates} (or \code{hasUndefinedLabels}).  Similarly, ES12-2 also
contains three bugs caused by the exactly same reason in same abstract
algorithms for \jscode{try} statements.

The bug in ES12-3 is a reference bug for an already defined variable
\code{index} in the abstract algorithm \textbf{CreateMappedArgumentsObject}.
For each function call in JavaScript programs, an \jscode{arguments} object is
created by \textbf{CreateMappedArgumentsObject}.  In the algorithm, the variable
\code{index} is defined to handle the index of a given list of arguments.
However, the variable is defined twice in step 14 and 17 of the algorithm.

ES12-4 contains two reference bugs for already defined variable \code{succeeded}
in \textbf{DefineOwnProperty} of \jscode{Array} objects and
\textbf{ArraySetLength}.  The \jscode{Array} objects are exotic, which means
that they are not ordinary objects and have special algorithms for specific
behaviors.  The two algorithms are wrapper algorithms of
\textbf{OrdinaryDefineOwnProperty} which updates object properties.  They define
the variable \code{succeeded} to represent the result of
\textbf{OrdinaryDefineOwnProperty}.  However, the variable is defined twice in a
specific condition.

@@

The bug in ES12-6 is a reference bug for unknown variable \code{ClassHeritage}
in \textbf{Contains} for tails of \jscode{class} declarations.  A tail of
\jscode{class} declaration consists of an optional class heritage with
\jscode{extends} keyword and a class body enclosed by curly braces.  When the
optional class heritage does not exist, the variable \code{ClassHeritage} is not
defined but the \textbf{Contains} algorithm tries to access it without any check
of its existence.
